### 2014-03-02 paper/intro.tex
wc
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
paren
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

A defining aspect of web platforms is the combinability of many
components of various providence.  This pattern shows up in browser
extensions, which run JavaScript code alongside third-party website
code, web applications, which include possibly untrusted third-party
libraries, and mash-up websites, which combine code and data from
websites which may not even be aware of each other's existence.  While
this combinability has offered great flexibility, it also poses a set of
unique security challenges: in particular, maintaining the privacy of
data in these settings is difficult, if not impossible.

>>>>

A defining aspect of web platforms is the combinability of
components of differing providence.  This pattern shows up in browser
extensions (which run JavaScript code alongside third-party website
code), web applications (which include possibly untrusted third-party
libraries), and mash-up websites (which combine code and data from
websites which may not even be aware of each other's existence.)  While
this combinability has offered great flexibility, it also poses a set of
unique security challenges: in particular, maintaining the privacy of
data in these settings is difficult, if not impossible.
